---
title: "Data Wrangling"
author: "Masoud Jasbi"
date: "`r Sys.Date()`"
output: pdf_document
---

This first chunk of code loads all the packages we need for data wrangling.

```{r packages, include=FALSE}
library(tidyverse)
```

# Loading and Inspecting the Data
#Load the data from csv. Replace the name "toy_data.csv" with the filename.

```{r loadRawData}
english_raw_data <- read_csv("english_fifty_participants.csv")
hungarian_raw_data <- read_csv("hungarian_fifty_participants.csv")
hungarian2_raw_data <- read_csv("hungarian2_fifty_participants.csv")

```

# Removing Useless Columns or Rows

In the template data, we have a first row that repeats column names and a second row that has additional test we don't want to use. We are going to remove these two rows. We are going to also remove the following columns that we don't intend to use: StartDate, EndDate, Status, IPAddress, Progress, RecordedDate, RecipientLastName, RecipientFirstName, RecipientEmail, ExternalReference, LocationLatitude, LocationLongitude.

```{r}
english_removed_data <- 
  english_raw_data[-c(1:2),] %>% #removing the first two rows
  select(-StartDate, -EndDate, -Status, -Progress, -RecordedDate) #removing colunns we don't need

hungarian_removed_data <- 
  hungarian_raw_data[-c(1:2),] %>% #removing the first two rows
  select(-StartDate, -EndDate, -Status, -Progress, -RecordedDate) #removing colunns we don't need

hungarian2_removed_data <- 
  hungarian2_raw_data[-c(1:2),] %>% #removing the first two rows
  select(-StartDate, -EndDate, -Status, -Progress, -RecordedDate) #removing colunns we don't need
```


# Exclusions

Here we explain the exclusion criteria for this study. We first removed participants that did not finish the task. We also removed preview runs of the study that were not actual participants providing the data but rather researchers testing the study.

```{r}
english_excluded_data <-
  english_removed_data %>%
  filter(Finished==1) %>% # removing participants that did not finish the task
  filter(DistributionChannel!="preview") %>% # removing trials that were preview trials
  select(-Finished, -DistributionChannel)
hungarian_excluded_data <-
  hungarian_removed_data %>%
  filter(Finished==1) %>% # removing participants that did not finish the task
  filter(DistributionChannel!="preview") %>% # removing trials that were preview trials
  select(-Finished, -DistributionChannel)
hungarian2_excluded_data <-
  hungarian2_removed_data %>%
  filter(Finished==1) %>% # removing participants that did not finish the task
  filter(DistributionChannel!="preview") %>% # removing trials that were preview trials
  select(-Finished, -DistributionChannel)
```

The next chunk saves the data that was excluded. 

```{r}
english_exclusions <-
  english_removed_data %>%
  filter(Finished==0 | DistributionChannel=="preview") # removing participants that did not finish the task
hungarian_exclusions <-
  hungarian_removed_data %>%
  filter(Finished==0 | DistributionChannel=="preview") # removing participants that did not finish the task
hungarian2_exclusions <-
  hungarian2_removed_data %>%
  filter(Finished==0 | DistributionChannel=="preview") # removing participants that did not finish the task
```

# Reshaping the data into Tidy Form

```{r}
english_tidy_data <-
  english_excluded_data %>%
  gather("question", "response", Control_noanimals_1:not_and_dc_102)
hungarian_tidy_data <-
  hungarian_excluded_data %>%
  gather("question", "response", Control_noanimals_1:not_and_dc_102)
hungarian2_tidy_data <-
  hungarian2_excluded_data %>%
  gather("question", "response", Control_noanimals_1:not_and_dc_102)
```

# Saving the Tidy Data

Here we save the data that is reading for ploting and statistical analyses.

```{r}
write_csv(english_tidy_data, "english_tidydata.csv")
write_csv(hungarian_tidy_data, "hungarian_tidydata.csv")
write_csv(hungarian2_tidy_data, "hungarian2_tidydata.csv")

```


```






