---
title: "Template Plots"
author: "Masoud Jasbi"
date: "`r Sys.Date()`"
output: pdf_document
---
#Load the necessary packages

```{r packages, include=FALSE} 

```

# Load Tidy Data that was created at the end of data wrangling, and change the numeric values in the response column to readable values. 

``` {r}


# Read the CSV file
english_tidy_data <- read.csv("english_tidydata.csv", stringsAsFactors = FALSE)
hungarian_tidy_data <- read.csv("hungarian_tidydata.csv", stringsAsFactors = FALSE)
hungarian2_tidy_data <- read.csv("hungarian2_tidydata.csv", stringsAsFactors = FALSE)

# Define mapping of numbers to text
# This is the order of the cards in Qualtrics. The species of the animals varies (cat, dog, bird, elephant), but the order of the card is always the same: the first card has the first animal, the second card has the second animal, the third card has no animals, and the fourth card has both animals from the first and second cards. 

mapping <- c("1" = "animal 1", "2" = "animal 2", "3" = "no animal", "4" = "both animals")

# Function to replace numbers with text
replace_numbers <- function(x) {
  numbers <- unlist(str_extract_all(as.character(x), "\\d+"))  # Extract all numbers
  if (length(numbers) > 0) {
    return(paste(mapping[numbers], collapse = ", "))  # Replace and join with ", "
  } else {
    return(x)  # Return unchanged if no numbers found
  }
}

# Apply the function to the response column in the tidy_data
english_tidy_data$response <- sapply(english_tidy_data$response, replace_numbers)
hungarian_tidy_data$response <- sapply(hungarian_tidy_data$response, replace_numbers)
hungarian2_tidy_data$response <- sapply(hungarian2_tidy_data$response, replace_numbers)

# Save the modified data into a csv. 
write.csv(english_tidy_data, "english_tidydata_modified.csv", row.names = FALSE)
write.csv(hungarian_tidy_data, "hungarian_tidydata_modified.csv", row.names = FALSE)
write.csv(hungarian2_tidy_data, "hungarian2_tidydata_modified.csv", row.names = FALSE)
```

#Plotting the data

```{r}
#extracting the data without the "control" suffix
#Load experimental data from the modified tidy data. 
english_modified_tidy_data <- read.csv("english_tidydata_modified.csv")
hungarian_modified_tidy_data <- read.csv("hungarian_tidydata_modified.csv")
hungarian2_modified_tidy_data <- read.csv("hungarian2_tidydata_modified.csv")

english_experimental_data <- english_modified_tidy_data %>%
    filter(!grepl("^Control", question))
hungarian_experimental_data <- hungarian_modified_tidy_data %>%
    filter(!grepl("^Control", question))
hungarian2_experimental_data <- hungarian2_modified_tidy_data %>%
    filter(!grepl("^Control", question))

#separata the question names from their stress number. 
#name example: not_and_eb_001, not_and_eb_101. The function below separates the name not_and_eb from the number. 
#the number at the end of the name is the stress number. If the first number is zero (001), then "not"is stressed. 
#if the first number is 1 (101), then the coordinating conjunction is stressed. 

english_experimental_data <- english_experimental_data %>%
  separate(question, into = c("not", "conjunction", "animals", "stress_number"), 
           sep = "_", fill = "right")
english_experimental_data <- english_experimental_data %>%
  mutate(not_conjunction = paste(not, conjunction, sep = "_"))
english_experimental_data <- english_experimental_data %>%
  select(-not, -conjunction)

hungarian_experimental_data <- hungarian_experimental_data %>%
  separate(question, into = c("not", "conjunction", "animals", "stress_number"), 
           sep = "_", fill = "right")
hungarian_experimental_data <- hungarian_experimental_data %>%
  mutate(not_conjunction = paste(not, conjunction, sep = "_"))
hungarian_experimental_data <- hungarian_experimental_data %>%
  select(-not, -conjunction)

hungarian2_experimental_data <- hungarian2_experimental_data %>%
  separate(question, into = c("not", "conjunction", "animals", "stress_number"), 
           sep = "_", fill = "right")
hungarian2_experimental_data <- hungarian2_experimental_data %>%
  mutate(not_conjunction = paste(not, conjunction, sep = "_"))
hungarian2_experimental_data <- hungarian2_experimental_data %>%
  select(-not, -conjunction)


#create question groups by the stress number. 

english_experimental_data <- english_experimental_data %>%
  mutate(group_combined = case_when(
    not_conjunction == "not_or" & stress_number %in% c("001", "002", "003") ~ "NOT_or",
    not_conjunction == "not_or" & stress_number %in% c(101, 102, 103) ~ "not_OR",
    not_conjunction == "not_and" & stress_number %in% c("001", "002", "003") ~ "NOT_and",
    not_conjunction == "not_and" & stress_number %in% c(101, 102, 103) ~ "not_AND",
    TRUE ~ not_conjunction 
  ))
hungarian_experimental_data <- hungarian_experimental_data %>%
  mutate(group_combined = case_when(
    not_conjunction == "not_or" & stress_number %in% c("001", "002", "003") ~ "NOT_or",
    not_conjunction == "not_or" & stress_number %in% c(101, 102, 103) ~ "not_OR",
    not_conjunction == "not_and" & stress_number %in% c("001", "002", "003") ~ "NOT_and",
    not_conjunction == "not_and" & stress_number %in% c(101, 102, 103) ~ "not_AND",
    TRUE ~ not_conjunction 
  ))
hungarian2_experimental_data <- hungarian2_experimental_data %>%
  mutate(group_combined = case_when(
    not_conjunction == "not_or" & stress_number %in% c("001", "002", "003") ~ "NOT_or",
    not_conjunction == "not_or" & stress_number %in% c(101, 102, 103) ~ "not_OR",
    not_conjunction == "not_and" & stress_number %in% c("001", "002", "003") ~ "NOT_and",
    not_conjunction == "not_and" & stress_number %in% c(101, 102, 103) ~ "not_AND",
    TRUE ~ not_conjunction 
  ))

write_csv(english_experimental_data, "english_experimental_data.csv")
write_csv(hungarian_experimental_data, "hungarian_experimental_data.csv")
write_csv(hungarian2_experimental_data, "hungarian2_experimental_data.csv")

# Calculate proportions
english_data_summary <- english_experimental_data %>%
  group_by(group_combined, response) %>%
  summarize(count = n()) %>%
  mutate(proportion = count / sum(count))
hungarian_data_summary <- hungarian_experimental_data %>%
  group_by(group_combined, response) %>%
  summarize(count = n()) %>%
  mutate(proportion = count / sum(count))
hungarian2_data_summary <- hungarian2_experimental_data %>%
  group_by(group_combined, response) %>%
  summarize(count = n()) %>%
  mutate(proportion = count / sum(count))

#write the data summary into a csv

write_csv(english_data_summary, "english_data_summary.csv")
write_csv(hungarian_data_summary, "hungarian_data_summary.csv")
write_csv(hungarian2_data_summary, "hungarian2_data_summary.csv")

# define custom colors
custom_colors <- c(
  "animal 1, animal 2" = "#808080",        # Medium gray
  "animal 1, animal 2, no animal" = "#FFD200",  # UC Davis gold
  "animal 1, no animal" = "#94BFA2",       # Cool green
  "animal 2" = "#2F4858",                  # Deep slate
  "animal 2, no animal" = "#A5C8E1",       # Soft blue
  "both animals" = "#F1F1F1",              # Pale gray
  "no animal" = "#002855",                # UC Davis blue
  "NA" = "#D0D0D0"                         # Light gray
)

# Create the stacked bar plot
ggplot(english_data_summary, aes(x = group_combined, 
                         y = proportion, 
                         fill = as.factor(response))) + 
  geom_bar(stat = "identity") +
  scale_fill_manual(values = custom_colors) +
  labs(x = "Question Group", 
       y = "Proportion of Responses", 
       fill = "Response") +
  theme_bw(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "right",
    legend.title = element_text(size = 14, face = "bold"),
    legend.text = element_text(size = 12),
    panel.grid.major = element_line(color = "gray90"),
    panel.grid.minor = element_blank()
  )
ggplot(hungarian_data_summary, aes(x = group_combined, 
                         y = proportion, 
                         fill = as.factor(response))) + 
  geom_bar(stat = "identity") +
  scale_fill_manual(values = custom_colors) +
  labs(x = "Question Group", 
       y = "Proportion of Responses", 
       fill = "Response") +
  theme_bw(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "right",
    legend.title = element_text(size = 14, face = "bold"),
    legend.text = element_text(size = 12),
    panel.grid.major = element_line(color = "gray90"),
    panel.grid.minor = element_blank()
  )
ggplot(hungarian2_data_summary, aes(x = group_combined, 
                         y = proportion, 
                         fill = as.factor(response))) + 
  geom_bar(stat = "identity") +
  scale_fill_manual(values = custom_colors) +
  labs(x = "Question Group", 
       y = "Proportion of Responses", 
       fill = "Response") +
  theme_bw(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "right",
    legend.title = element_text(size = 14, face = "bold"),
    legend.text = element_text(size = 12),
    panel.grid.major = element_line(color = "gray90"),
    panel.grid.minor = element_blank()
  )


# Create the stacked bar plot
ggplot(english_data_summary, aes(x = group_combined, 
                        y = proportion, 
                        fill = as.factor(response))) + 
  geom_bar(stat = "identity") +
  labs(x = "Question Group", 
       y = "Proportion of Responses", 
       fill = "Response") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggplot(hungarian_data_summary, aes(x = group_combined, 
                        y = proportion, 
                        fill = as.factor(response))) + 
  geom_bar(stat = "identity") +
  labs(x = "Question Group", 
       y = "Proportion of Responses", 
       fill = "Response") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggplot(hungarian2_data_summary, aes(x = group_combined, 
                        y = proportion, 
                        fill = as.factor(response))) + 
  geom_bar(stat = "identity") +
  labs(x = "Question Group", 
       y = "Proportion of Responses", 
       fill = "Response") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```


```{r}
#creating the plot for the control data

#filter control data from the modified tidy data
english_control_data <- english_modified_tidy_data %>%
    filter(grepl("^Control", question))

english_control_data <- english_control_data %>%
  separate(question, into = c("control", "name", "number"), 
           sep = "_", fill = "right")
hungarian_control_data <- hungarian_modified_tidy_data %>%
    filter(grepl("^Control", question))

hungarian_control_data <- hungarian_control_data %>%
  separate(question, into = c("control", "name", "number"), 
           sep = "_", fill = "right")
hungarian2_control_data <- hungarian2_modified_tidy_data %>%
    filter(grepl("^Control", question))

hungarian2_control_data <- hungarian2_control_data %>%
  separate(question, into = c("control", "name", "number"), 
           sep = "_", fill = "right")

#Create the stacked bar plot for the control data
english_control_plot <- english_control_data %>%
    group_by(name, response) %>%
    summarize(count = n(), .groups = "drop") %>%
    mutate(proportion = count / sum(count)) %>%
    ggplot(aes(x = name, y = proportion, fill = as.factor(response))) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = "Control Questions",
         x = "Question",
         y = "Proportion of Responses",
         fill = "Response") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
hungarian_control_plot <- hungarian_control_data %>%
    group_by(name, response) %>%
    summarize(count = n(), .groups = "drop") %>%
    mutate(proportion = count / sum(count)) %>%
    ggplot(aes(x = name, y = proportion, fill = as.factor(response))) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = "Control Questions",
         x = "Question",
         y = "Proportion of Responses",
         fill = "Response") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
hungarian2_control_plot <- hungarian2_control_data %>%
    group_by(name, response) %>%
    summarize(count = n(), .groups = "drop") %>%
    mutate(proportion = count / sum(count)) %>%
    ggplot(aes(x = name, y = proportion, fill = as.factor(response))) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = "Control Questions",
         x = "Question",
         y = "Proportion of Responses",
         fill = "Response") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(english_control_plot)
print(hungarian2_control_plot)
print(hungarian_control_plot)
```
```{r}


# Read the data
english_df <- read.csv("english_experimental_data.csv")
hungarian_df <- read.csv("hungarian_experimental_data.csv")
hungarian2_df <- read.csv("hungarian2_experimental_data.csv")

# Convert response to factor (required for categorical family)
english_df$response <- as.factor(english_df$response)

english_fit <- brm(
  formula = response ~ group_combined,
  family = categorical(),
  data = english_df
)
# Read the data


# Convert response to factor (required for categorical family)
hungarian_df$response <- as.factor(hungarian_df$response)

hungarian_fit <- brm(
  formula = response ~ group_combined,
  family = categorical(),
  data = hungarian_df
)
# Read the data


# Convert response to factor (required for categorical family)
hungarian2_df$response <- as.factor(hungarian2_df$response)

hungarian2_fit <- brm(
  formula = response ~ group_combined,
  family = categorical(),
  data = hungarian2_df
)


```

```{r}
  # Posterior predictive check
ce <- conditional_effects(english_fit, categorical = TRUE)
plot(ce, plot = TRUE)

# Posterior predictive check
ce <- conditional_effects(hungarian_fit, categorical = TRUE)
plot(ce, plot = TRUE)

# Posterior predictive check
ce <- conditional_effects(hungarian2_fit, categorical = TRUE)
plot(ce, plot = TRUE)

```
#should we include "animal 1, animal 2" and 'animal 1, animal 2, no animal" into joint denial? 
#I want to formalize the response types for easy comparison and similar coloring, but I am not sure whether to put "animal 1, animal 2" into other, or joint denial. 



